---
title: "calcUnique Package"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(calcUnique)

```


This is a one-function package so that you can pass only unique values to a computationally expensive function that returns an output of the same length as the input.

In importing and working with tidy data, it is common to have index columns, often including time stamps
that are far from unique. Some funcitons to work with these such as text conversion, various `grep()`-based
functions, and often the `cut()` function are relatively slow when working with tens of millions of rows or more.

This wrapper function pares down the input vector to process to only unique values using hte `unique()` function, and 
in my experience the `unique()` and `match()` functions upon which `calcUnique()` is based are so fast that
only a small amount of repition is necessary to make calcUnique the faster option.

`calcUnique()` is a wrapper for any function that takes in a vector or list and returns a vector or list the same length. The inputs and outputs are the same as they would be otherwise ... it just happens faster.

## Examples:

```{r calcUnique_examples}

#Create a sample of some date text with repeats
ts_sample <-
  sample(as.character(seq(
    from = as.POSIXct('2020-03-01'),
    to = as.POSIXct('2020-03-05'),
    by = 'day'
  )),
  size = 10, replace = TRUE)

ts_sample

#Now convert the time text back to POSIXct timestamps:
as.POSIXct(ts_sample)

#Do the same with the calcUnique function:
calcUnique(ts_sample, as.POSIXct)

#Just to show that the output is the same with and without calcUnique:
all.equal(as.POSIXct(ts_sample), calcUnique(ts_sample, as.POSIXct))

#An example for when the function doesn't take the vector as the first argument:
gsub("03", "$3", ts_sample)
calcUnique(ts_sample, function(i) gsub("03", "$3", i))

```

